Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-06-21 Paper.tex
An abbreviation abbreviates but does not imply

&&&& where division is not subject to modulo $2^{256}$. \\

@@

&&&& Where all values are treated as two's complement signed 256-bit integers and division is not subject to modulo $2^{256}.$ \\

@@

&&&& where $\mod$ is not subject to modulo $2^{256}$. \\

@@

&&&& Where all values are treated as two's complement signed 256-bit integers and $\mod$ is not subject to modulo $2^{256}$. \\

>>>>

@@

&&&& Where all values are treated as two's complement signed 256-bit integers. \\

@@

@@

&&&& Where all values are treated as two's complement signed 256-bit integers. \\
